State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-04 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
add Matlab code for filter and model to src/Matlab
updated matlab code
analytic sensor and basis charactristics  plot

\begin{figure}
	\label{fig:FreqAnalysis} 
	\begin{center}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/BasisChar.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/SensorChar.pdf}}
\subfigure[][]{\includegraphics[width=1.8in]{./Graph/ObservationFrequencyResponse.pdf}}\\
	\end{center}
	\caption{Frequency analysis of the. \textbf{a.} The spatial frequency response of a 1-dimensional neural field basis functions project. The symmetry of the field basis functions, connectivity kernel basis functions and sensors allow for the 1-dimensional representation of the spectral characteristics. The dashed line shows the cut-off frequency (-3 dB point). \textbf{b} The spatial frequency response of a 1-dimensional model sensor. The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function. \textbf{c.} Two 2-dimensional spatial frequency (in power dB, averaged over 200 time steps) of the observed field.} 
\end{figure}
Following this, the distance between basis function, $\Delta_{phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum. \mike{Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.}

>>>>

\begin{figure*}
	\label{fig:FreqAnalysis} 
	\begin{center}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/BasisChar.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/SensorChar.pdf}}
\subfigure[][]{\includegraphics[width=1.8in]{./Graph/ObservationFrequencyResponse.pdf}}\\
	\end{center}
	\caption{Frequency analysis of the. \textbf{a.} The spatial frequency response of a 1-dimensional neural field basis functions project. The symmetry of the field basis functions, connectivity kernel basis functions and sensors allow for the 1-dimensional representation of the spectral characteristics. The dashed line shows the cut-off frequency (-3 dB point). \textbf{b} The spatial frequency response of a 1-dimensional model sensor. The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function. \textbf{c.} Two 2-dimensional spatial frequency (in power dB, averaged over 200 time steps) of the observed field.} 
\end{figure*}
Following this, the distance between basis function, $\Delta_{phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum. \mike{Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.}
